Dark Control:\\ A Unified Account of Default Mode Function\\ by Control Theory and Reinforcement Learning

### 2017-04-30 paper/paper.tex
Figure RL => ODP/PDF + Bigger font size
Solve emdash "—" => \textemdash

%\renewcommand{\labelitemi}{--}

@@

\subsection{The hippocampus: memory, space, and experience replay}
The DMN midline is probably closely linked
with the HC in the medial temporal lobe \citep{vincet2006, shannon2013morning} --
a region long known to be involved in
memory operations and spatial navigation in animals and humans.

@@

\begin{wrapfigure}{r}{.4\linewidth}
  \caption{\textbf{Reinforcement learning in a nutshell.} Given the current state of the environment,
    the agent takes an action (by following some policy). This yields a reward and an observed
    state transition of the environment. This process goes on until interrupted or a goal state is reached.
    \textbf{XXX Please increase size of the font in the figure}}
  \centering
  \includegraphics[width=1.\linewidth]{rl.png}
  \label{fig:rl}
\end{wrapfigure}

RL is a problem-solving technique in which,
through repeated interactions with an unknown \textit{environment},
an agent learns to reach goals and optimize reward signals
in an iterative trial-and-error fashion (Fig. \ref{fig:rl}).
At a given moment, each taken \textit{action} $a$ triggers a change
in the \textit{state} of the environment
$s \rightarrow s'$, accompanied by environmental feedback signals as \textit{reward}
$r = r(s, a)$ collected by the agent (Fig. \ref{fig:rl}).
If the collected reward outcome yields a negative value it can be
more naturally interpreted as \textit{punishment}.
In this view, the environment is partially controlled by
the action of the agent and the reward can be thought
of as satisfaction -- or aversion -- accompanying the execution of
an action.
Action may be delayed to achieve substantial increases in expected reward
that is expected to grow with time.

@@

\subsubsection{Self-training and the loss function}
Successful learning in brains and computer algorithms is challenging without a
defined learning goal -- the \textit{loss function}.
The action $a$ chosen in state $s$ according to the policy matrix defined in
\eqref{eq:policy} yields a reward $r$ collected by the agent,
% (measured on their internal currency of worldly values ?),
after which the environment transitions to a new state $s' \in \mathcal S$.
% \textbf{XXX Please try to smoothen the previous sentence}
One such cycle yields a new \textit{experience} $e = (s,a,r,s')$.
Each cycle represents a behavior unit of the agent
and is recorded in replay memory buffer -- which we hypothesize to be the
HC --, possibly discarding the oldest entries to make space:
$\mathcal D \leftarrow \text{append}(\mathcal D, e)$.

@@

\subsubsection{Optimal control via stochastic gradient descent in the DMN}
Efficient learning of the entire set of model parameters can effectively be achieved
via \textit{gradient descent}.
\textbf{XXX Please add one explanatory sentence for GD.}
Reward prediction errors -- also known as \textit{regret}-- percolate
from lower to higher processing layers to modulate the choice of future actions

>>>>

@@

\subsection{The hippocampus: memory, space, and experience replay}
The DMN midline is probably closely linked
with the HC in the medial temporal lobe \citep{vincet2006, shannon2013morning} \textemdash
a region long known to be involved in
memory operations and spatial navigation in animals and humans.

@@

\begin{wrapfigure}{r}{.4\linewidth}
  \caption{\textbf{Reinforcement learning in a nutshell.} Given the current state of the environment,
    the agent takes an action (by following some policy). This yields a reward and an observed
    state transition of the environment. This process goes on until interrupted or a goal state is reached.}
  \centering
  \includegraphics[width=1.\linewidth]{rl.pdf}
  \label{fig:rl}
\end{wrapfigure}

RL is a problem-solving technique in which,
through repeated interactions with an unknown \textit{environment},
an agent learns to reach goals and optimize reward signals
in an iterative trial-and-error fashion (Fig. \ref{fig:rl}).
At a given moment, each taken \textit{action} $a$ triggers a change
in the \textit{state} of the environment
$s \rightarrow s'$, accompanied by environmental feedback signals as \textit{reward}
$r = r(s, a)$ collected by the agent (Fig. \ref{fig:rl}).
If the collected reward outcome yields a negative value it can be
more naturally interpreted as \textit{punishment}.
In this view, the environment is partially controlled by
the action of the agent and the reward can be thought
of as satisfaction \textemdash or aversion \textemdash accompanying the execution of
an action.
Action may be delayed to achieve substantial increases in expected reward
that is expected to grow with time.

@@

\subsubsection{Self-training and the loss function}
Successful learning in brains and computer algorithms is challenging without a
defined learning goal \textemdash the \textit{loss function}.
The action $a$ chosen in state $s$ according to the policy matrix defined in
\eqref{eq:policy} yields a reward $r$ collected by the agent,
% (measured on their internal currency of worldly values ?),
after which the environment transitions to a new state $s' \in \mathcal S$.
% \textbf{XXX Please try to smoothen the previous sentence}
One such cycle yields a new \textit{experience} $e = (s,a,r,s')$.
Each cycle represents a behavior unit of the agent
and is recorded in replay memory buffer \textemdash which we hypothesize to be the
HC \textemdash, possibly discarding the oldest entries to make space:
$\mathcal D \leftarrow \text{append}(\mathcal D, e)$.

@@

\subsubsection{Optimal control via stochastic gradient descent in the DMN}
Efficient learning of the entire set of model parameters can effectively be achieved
via \textit{gradient descent}.
\textbf{XXX Please add one explanatory sentence for GD.}
Reward prediction errors \textemdash also known as \textit{regret}\textemdash percolate
from lower to higher processing layers to modulate the choice of future actions
